--- 
title: "AP^&reg;^ Statistics Syllabus"
author: ""
date: "2019--2020"
site: bookdown::bookdown_site
output: 
  bookdown::gitbook:
    toc_depth: 2
    config:
      sharing: null
        # facebook: false
        # twitter: false
documentclass: article
fontsize: 12pt
#toc: no
bibliography: [book.bib, packages.bib]
csl: apa.csl
link-citations: yes
github-repo: ap-statistics/syllabus-docs
description: "This notebook includes a syllabus and detailed course schedule for AP Statistics."
always_allow_html: yes
classoption: fleqn
subparagraph: yes
# classoption: twocolumn
---

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, dev='png')
mon <- as.Date("2016-08-15")
# fri <- as.Date("2016-01-08")

advdate <- function(obj, adv) {
 tmon <- obj + 7*(adv-1)
 tfri <- obj + 4 + 7*(adv-1)
 tmon <- format(tmon, format="%m/%d")
 tfri <- format(tfri, format="%m/%d")
 zadv <- sprintf("%02d", adv)
 tmp <- paste("Week ",zadv,sep='',", ", tmon," - ",tfri)
 return(tmp)
}

library(RefManageR)
# library(knitcitations)
# library(rcrossref)
bib <- ReadBib("book.bib")
BibOptions(bib.style = "authoryear", style="markdown", first.inits=FALSE, max.names = 4, check.entries = FALSE)

#https://stackoverflow.com/questions/46260431/include-the-text-of-a-bibentry-in-the-rmarkdown-text-body-output
library(bibtex)
biblio <- bibtex::read.bib(file="book.bib")
```
# Course Description

AP^&reg;^ Statistics is a one-year course that covers descriptive statistics, probability theory, and statistical inference. In addition to TI-84 calculator sessions that align with the AP^&reg;^ Statistics curriculum, this course will also include supplementary R lab sessions to introduce students to statistical programming.


# Contact Information

**Teacher**: Mr. Li

**Course Website**: [https://ap-statistics.github.io](https://ap-statistics.github.io){target="_blank"}

**Office Hours**: [https://ap-statistics.github.io/#officehours](https://ap-statistics.github.io/#officehours){target="_blank"}

  * You are welcome to stop by anytime during scheduled office hours without an appointment.
  * If I need to reschedule office hours, I will send an e-mail to the class.
  * If you cannot make it to my office hours, please [schedule an appointment](https://ap-statistics.github.io/#officehours){target="_blank"}. If none of the time slots work for you, check with me after class so we can arrange a time to meet.
  
# Course Objectives

1. Develop mastery in descriptive and inference statistics.
2. Learn all relevant TI-84 calculator functions for the AP exam.
3. Gain exposure to statistical programming using R.



